The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-13 manuscript/manuscript.Rnw
add opossum and elephant transcriptome tables

\subsection{Elephant Placenta Transcriptome}

@@

>>>>

\subsection{African Elephant Placenta Transcriptome}

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
top.elephant.genes <- top.genes.table(species.name="loxodonta africana")
print(xtable(top.elephant.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.elephant.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 non-mitochondrial genes in
  \textit{Loxodonta africana}}
\label{tab:top50_elphant_placenta}
\end{wraptable}

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.opossum.expressed.genes,echo=FALSE,results="asis">>=
top.opossum.genes <- top.genes.table(species.name="monodelphis domestica")
print(xtable(top.opossum.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.opossum.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 non-mitochondrial genes in
  \textit{Monodelphis domestica}}
\label{tab:top50_opossum_placenta}
\end{wraptable}
